Verifying Demonstrations

### 2020-03-13 paper/DB-Schnorr-PKI.tex

There are two questions we must answer about this protocol:
\begin{enumerate}
  \item\label{DBSHW-MITM} Can the adversary perform \iac{MITM} attack against 
    the \ac{DHKE}?
  \item\label{DBSHW-anon} Does \(\XDHCL\) break anonymity?
\end{enumerate}

>>>>

There are two questions we must answer about this protocol:
\begin{enumerate}
  \item\label{DBSHW-MITM} Can the adversary perform \iac{MITM} attack against 
    the \ac{DHKE}?
  \item\label{DBSHW-anon} Does \(\XDHCL\) break anonymity?
\end{enumerate}
To justify the first question, we use a plain \ac{DHKE} to agree on \(k\), 
start using \(k\) for \ac{DB} and during the \ac{DB} do the authentication.
To justify the second question, we use CL04 anonymous 
credentials~\cite{CLsignatures}.
These provide anonymity.
However, revealing \(\XDHCL = \XDH^{\sk}\) is not part of CL04.
So we must show that \(\XDHCL\) maintains anonymity.
